Modeling thermal dust emission with the {\it PLANCK} 2015 release maps

### 2015-06-25 ms.tex
first pass at bitmask table
added DIRBE correlation slope figure

@@

>>>>

\begin{figure*}
\begin{center}
\epsfig{file=fig/dirbe_slopes.eps, width=6.5in}
\caption{\label{fig:dirbe_slopes} Linear fits of SFD-reprocessed DIRBE
240$\mu$m (left), 140$\mu$m (center), and 100$\mu$m (right) as a function of
\PLANCK~857 GHz. The red lines illustrate the DIRBE correlation slopes used in
our dust emission model optimization of $\S$\ref{sec:global}.}
\end{center}
\end{figure*}

@@

\begin{center}
\begin{deluxetable}{ll} 
\tabletypesize{\scriptsize}
\tablecolumns{2} 
\tablewidth{0pc} 
\tablecaption{\label{tab:bitmask} Bit-mask Summary} 
\tablehead{
\colhead{Bit} &
\colhead{Description}
}
\startdata
 0 & SFD compact source \\
 1 & SFD big object     \\
 2 & SFD no \IRAS       \\
 3 & SMICA inpainted    \\
 4 & CO emission        \\  %[-2ex]
\enddata
\end{deluxetable}
\end{center}
